The Anatomy of a Temporal Summarization System

### 2015-05-29 results.tex
spellinggit add acl2015.tex conclusion.tex dataset.tex experiments.tex introduction.tex methods.tex relatedwork.tex results.tex rouge_cum.tex nuggets-metrics-eps-converted-to.pdf rouge-time-eps-converted-to.pdf !

Table~\ref{tab:rouge} shows our results for system output samples against the full summary of nuggets using ROUGE. 
%shows our results for the evaluation using ROUGE. 
%AP+Salience shows improvement on ngram precision and recall over the 
%baselines. 
This improvement is statistically significant for all ngram
precision, recall, and F-measures
at the $\alpha = .01$ level
using the Wilcoxon signed-rank test.

@@

AP+Salience maintains its performance above the baselines over time as well. Figure~\ref{fig:trouge}
shows the ROUGE-1 scores over time. 
We show the difference in unigram precision (bigram precision is not shown but it follows
similar curve).
Within the initial days of the event, AP+Salience is able to take the lead over the over 
systems in ngram precision. 
The AP+Salience model is better able to find salient updates
earlier on; for the disaster domain, this is an especially important quality of the model.

Moreover, the AP+Salience's recall is not diminished by the high precision and remains competitive with AP.
Over time AP+Salience's recall also begins to pull away, while the other models start to suffer
from topic drift.

@@

Figure~\ref{fig:nperf} shows the expected gain across a range of 
similarity thresholds, where thresholds closer to 1 are more conservative
estimates. The ranking of the systems remains constant across the 
sweep with 
AP+Salience beating all baseline systems.
Predicting salience in general is helpful for keeping a summary on topic as
the RS approach out performs the clustering only approaches
on expected gain.

When looking at the comprehensiveness of the summaries AP outperforms
 AP+Salience. The compromise encoded in the AP+Salience objective
function, between being representative and being salient, is seen clearly here
where the performance of the AP+Salience methods is lower bounded by 
the salience focused RS
system and upper bounded by the clustering only AP system.
Overall, AP+Salience achieves the best balance of these two metrics.

@@

Table~\ref{tab:farouge} shows the results of our feature ablation
tests. Removing the language models yields a statistically 
significant drop in both ngram recall and F-measure. 
Interestingly, removing the basic features leads to an
increase in both unigram and bigram precision; in the bigram
case this is enough to cause a statistically significant increase
in F-measure over the full model. In other words, the generic features
actually lead to an inferior model when we can incorporate more appropriate
domain specific features.
The result mirrors Sparck Jones' claim that generic approaches to summarization cannot produce a useful summary \cite{ksj98}.
%This result mirrors Sparck Jones' claim that summarization should be in service of a purpose~\cite{?}.

Removing the language model and geographic relevance features leads to a
statistically significant drop in ROUGE-1 F1 scores. Unfortunately,
this is not the case for the temporal relevance features. We surmise that
these features are too strongly correlated with each other, 
i.e. the differences in TFIDF between hours are definitely not IID variables.

>>>>

Table~\ref{tab:rouge} shows our results for system output samples against the 
full summary of nuggets using ROUGE. This improvement is statistically 
significant for all ngram precision, recall, and F-measures at the 
$\alpha = .01$ level using the Wilcoxon signed-rank test.

@@

\textsc{AP+Salience} maintains its performance above the baselines over time 
as well. Figure~\ref{fig:trouge} shows the ROUGE-1 scores over time. We show 
the difference in unigram precision (bigram precision is not shown but it 
follows similar curve). Within the initial days of the event, 
\textsc{AP+Salience} is able to take the lead over the over systems in ngram 
precision. The \textsc{AP+Salience} model is better able to find salient 
updates earlier on; for the disaster domain, this is an especially important 
quality of the model.

Moreover, the \textsc{AP+Salience}'s recall is not diminished by the high 
precision and remains competitive with \textsc{AP}. Over time 
\textsc{AP+Salience}'s recall also begins to pull away, while the other models
start to suffer from topic drift.

@@

Figure~\ref{fig:nperf} shows the expected gain across a range of similarity 
thresholds, where thresholds closer to 1 are more conservative estimates. 
The ranking of the systems remains constant across the sweep with 
\textsc{AP+Salience} beating all baseline systems. Predicting salience in 
general is helpful for keeping a summary on topic as the \textsc{RS} approach 
out performs the clustering only approaches on expected gain.

When looking at the comprehensiveness of the summaries \textsc{AP} outperforms
\textsc{AP+Salience}. The compromise encoded in the \textsc{AP+Salience} 
objective function, between being representative and being salient, is seen 
clearly here where the performance of the \textsc{AP+Salience} methods is 
lower bounded by the salience focused \textsc{RS} system and upper bounded by 
the clustering only \textsc{AP} system. Overall, \textsc{AP+Salience} achieves
the best balance of these two metrics.

@@

Table~\ref{tab:farouge} shows the results of our feature ablation tests. 
Removing the language models yields a statistically significant drop in both 
ngram recall and F-measure. Interestingly, removing the basic features leads 
to an increase in both unigram and bigram precision; in the bigram case this 
is enough to cause a statistically significant increase in F-measure over the 
full model. In other words, the generic features actually lead to an inferior 
model when we can incorporate more appropriate domain specific features.
The result mirrors Sparck Jones' claim that generic approaches to 
summarization cannot produce a useful summary \cite{ksj98}.

Removing the language model and geographic relevance features leads to a
statistically significant drop in ROUGE-1 F1 scores. Unfortunately,
this is not the case for the temporal relevance features. We surmise that
these features are too strongly correlated with each other, 
i.e. the differences in TF*IDF between hours are definitely not i.i.d. 
variables.
